Project report

### 2018-02-21 ProjectReport/BigDataHomework.tex
update report

	As in the Nearest Neighbours case, we have also included the html files in the gmplot folder. in \ref{subres} we show the total results for Nearest Subroutes.

	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\textbf{}  & \textbf{Time} & \textbf{id1} & \textbf{pts1} & \textbf{id2} & \textbf{pts2} & \textbf{id3} & \textbf{pts3} & \textbf{id4} & \textbf{pts4} & \textbf{id5} & \textbf{pts5} \\ \hline
			\textbf{1} & 05:346:265     & 211          & 31            & 728          & 31            & 3590         & 22            & 4985          & 21            & 843          & 19            \\ \hline
			\textbf{2} & 01:63:755     & 2620         & 42            & 510          & 37            & 1093         & 34            & 426          & 31            & 363          & 30            \\ \hline
			\textbf{3} & 00:32:319     & 200          & 40            & 1885         & 40            & 2763         & 40            & 142          & 39            & 135          & 35            \\ \hline
			\textbf{4} & 00:46:297     & 566          & 32            & 1269         & 21            & 227          & 20            & 2561         & 17            & 252          & 15            \\ \hline
			\textbf{5} & 00:57:303     & 940          & 33            & 1932         & 22            & 1384         & 21            & 1606         & 21            & 1822         & 20            \\ \hline
		\end{tabular}
	\caption{Nearest subroutes results}
	\label{subres}
	\end{table}

>>>>

	As in the Nearest Neighbours case, we have also included the html files in the gmplot folder. The automated way with phantomjs does not work always correctly and in above images the red points are not included in the images. However, in html files, all the common points are presented. In \ref{subres} we show the total results for Nearest Subroutes.

	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\textbf{}  & \textbf{Time} & \textbf{id1} & \textbf{pts1} & \textbf{id2} & \textbf{pts2} & \textbf{id3} & \textbf{pts3} & \textbf{id4} & \textbf{pts4} & \textbf{id5} & \textbf{pts5} \\ \hline
			\textbf{1} & 07:427:941     & 5152          & 125            & 5683          & 124            & 4621         & 118            & 593          & 116            & 278          & 111            \\ \hline
			\textbf{2} & 06:408:627     & 620         & 175            & 1078          & 136            & 4422         & 129            & 5079          & 126            & 2927          & 119            \\ \hline
			\textbf{3} & 03:226:050     & 3822          & 202            & 6401         & 136            & 1229         & 120            & 3028          & 111            & 2308          & 110            \\ \hline
			\textbf{4} & 05:305:995     & 6401          & 180            & 1249         & 111            & 1740          & 111            & 586         & 108            & 5858          & 105            \\ \hline
			\textbf{5} & 06:367:621     & 5010          & 144            & 723         & 129            & 1870         & 124            & 2792         & 115            & 4759         & 115            \\ \hline
		\end{tabular}
	\caption{Nearest subroutes results}
	\label{subres}
	\end{table}
